IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-13 paper/abstract.tex

\begin{abstract}
Many important security problems in JavaScript, such as browser extension
security, untrusted JavaScript libraries and
safe integration of mutually distrustful websites (mash-ups), may be effectively addressed using an efficient implementation
of information flow control.
We formally define a system in which a coarse-grained dynamic IFC system
can be designed once and then applied to any programming language
for which external effects can be controlled.  We use
this formalism to implement two IFC systems for JavaScript, and show how
it applies to other languages such as C.
We describe how this methodology offers design principles for
the construction of information flow control systems in more
traiditional settings, as well as compositional proofs for optimized
concrete implementations of IFC systems, which can be shown to
have interference by relating them to their fully isolated variants.
\end{abstract}

>>>>

\begin{abstract}
Many important security problems in JavaScript, such as browser
extension security, untrusted JavaScript libraries and safe
integration of mutually distrustful websites (mash-ups), may be
effectively addressed using an efficient implementation of information
flow control (IFC).  Unfortunately existing fine-grained approaches to
JavaScript IFC require modifications to the language semantics, a
non-goal for browser applications.  In this work we take the ideas of
coarse-grained dynamic IFC to the limit and provide the theoretical
foundation for a language-based approach that can be applied to any
programming language for which external effects can be controlled.  We
then apply this formalism to JavaScript, in the context of Node.js and
Firefox, and show how it generalizes to other language
implementations, including C and Haskell.  Our methodology offers
design principles for the construction of information flow control
systems when isolation can easily be achieved, as well as
compositional proofs for optimized concrete implementations of these
systems, by relating them to their fully isolated variants.
\end{abstract}

### 2014-10-13 paper/extensions.tex

Like labeled references, features with external effects must be
modeled in the IFC language; we must reason about the precise security
implications of features that otherwise inherently leak data.
%
Previous approaches have modeled external effects by internalizing the
effects as writes/reads to labeled channels/references~\cite{stefan:addressing-covert}.
%
An alternative approach is to model such effects as messages to/from
certain labeled tasks, an approach taken by our Node.js
implementation.
%
These ``special'' tasks are trusted with access to the unlabeled
primitives that can be used to perform the external effects; since the
interface to these tasks is already part of the IFC language, the
proof only requires showing that this task does not leak information.
%
An alternative approach of wrapping or modifying/restricting unsafe
primitives is, for example, used in COWL and JSFlow to allow for
controlled network communication.
%
By restricting the default XHR object, for example, COWL allows code
to communicate with hosts according to the task's current label.

>>>>

Like labeled references, features with external effects must be
modeled in the IFC language; we must reason about the precise security
implications of features that otherwise inherently leak data.
%
Previous approaches have modeled external effects by internalizing the
effects as writes/reads to labeled channels/references~\cite{stefan:addressing-covert}.
%
An alternative approach is to model such effects as messages to/from
certain labeled tasks, an approach taken by our Node.js
implementation.
%
These ``special'' tasks are trusted with access to the unlabeled
primitives that can be used to perform the external effects; since the
interface to these tasks is already part of the IFC language, the
proof only requires showing that this task does not leak information.
%
An alternative approach of restricting or wrapping unsafe primitives
is, for example, used in COWL and JSFlow, respectively, to allow for
controlled network communication.
%
(By restricting the default XHR object, for example, COWL allows code
to communicate with hosts according to the task's current label.)
